---
title: "Homework 1"
author: "Tongtong Zhu"
date: 2022-09-23
output: github_document
---

```{r loading_packages, message = FALSE}
library(tidyverse)
```

# Problem 1

```{r loading_data}
data("penguins", package = "palmerpenguins")
```

```{r mean of flipper length}
mean_flipper_length = mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
```

## Description of dataset

The `penguins` dataset has 344 observations of 8 variables. The eight variables include species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year.

It contains `r nrow(penguins)` rows and `r ncol(penguins)` columns. The mean flipper length is `r round(mean_flipper_length, digits =2)` mm.

## Scatterplot

```{r scatterplot, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point(na.rm = TRUE)

ggsave("scatter_plot.pdf", height = 4, width = 6)
```


# Problem 2

## Data frame

```{r df_create}
new_df = tibble(
  vec_numeric = rnorm(10, mean = 0, sd = 1),
  vec_logical = vec_numeric > 0,
  vec_char = c("A","B","C","D","E","F","G","H","I","J"),
  vec_factor = factor(rep(c("small", "medicum", "large"), length = 10))
)

```


## Mean of each variable

```{r mean of variables, warning = FALSE}
mean_num = mean(pull(new_df, vec_numeric))
mean_logical = mean(pull(new_df, vec_logical))
mean_char = mean(pull(new_df, vec_char))
mean_factor = mean(pull(new_df, vec_factor))

```

The mean of `vec_numeric` variable is `r round (mean_num, digits =2)`.   The mean of `vec_logical`variable is `r round (mean_logical, digits =2)`. The mean of `vec_char` variable is `r round (mean_char, digits =2)`.  The mean of `vec_factor` variable is `r round (mean_factor, digits =2)`.  

**Discussion**: The mean calculation works for numeric variable and logical variable, but does not work for character variable and factor variable.




